---
output: github_document
---
<!-- README.md is generated from README.Rmd. Please edit that file -->
# promR

[![Build Status](https://travis-ci.org/glenn-m/promR.svg?branch=master)](https://travis-ci.org/glenn-m/promR)

R library for reading and analysing metrics stored on a Prometheus server.

## Installation
```{r, echo = TRUE, eval = FALSE}
if (requireNamespace("devtools", quietly = TRUE)) {
    devtools::install_github('glenn-m/promR')
} else {
    install.packages("devtools")
    devtools::install_github('glenn-m/R')
}
```

## Usage

To retrieve the current value of the `http_requests_total` metric

```{r, echo = TRUE}
library(promR)
prom <- Prometheus$new(host = "http://demo.robustperception.io", port = 9090)
metrics <- prom$query(query = "http_requests_total", time = "2018-10-26T20:10:51.781Z")
```
**Output:**
```{r, echo = FALSE, results = 'asis'}
knitr::kable(head(metrics))
```

## Contributing
1.  Fork it ( https://github.com/glenn-m/promR/fork )
2.  Create your feature branch (git checkout -b my-new-feature)
3.  Make your changes
4.  Run `devtools::test()` to ensure tests are passing.
5.  Commit your changes (git commit -am 'Add some feature')
6.  Push to the branch (git push origin my-new-feature)
7.  Create a new Pull Request

## Contributors

- [Glenn McDonald](https://github.com/glenn-m)
- [Konrad Zdeb](https://github.com/konradedgar)
