---
output: github_document
---
<!-- README.md is generated from README.Rmd. Please edit that file -->
# promR

[![Build Status](https://travis-ci.org/glenn-m/promR.svg?branch=master)](https://travis-ci.org/glenn-m/promR) 
[![Coverage status](https://codecov.io/gh/glenn-m/promR/branch/master/graph/badge.svg)](https://codecov.io/github/glenn-m/promR?branch=master) [![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

R library for reading and analysing metrics stored on a [Prometheus](https://prometheus.io/) server.

## Installation

You can install `promR` using [`devtools`](https://github.com/r-lib/devtools):

```{r, echo = TRUE, eval = FALSE}
if (requireNamespace("devtools", quietly = TRUE)) {
    devtools::install_github('glenn-m/promR')
} else {
    install.packages("devtools")
    devtools::install_github('glenn-m/promR')
}
```

## Usage

To retrieve the value of the `go_goroutines` metric for the current time.

```{r, echo = TRUE}
library(promR)
prom <- Prometheus$new(host = "http://demo.robustperception.io", port = 9090)
metrics <- prom$query(query = "go_goroutines", time = format(Sys.time(),  "%Y-%m-%dT%H:%M:%SZ"))
```
**Output:**
```{r, echo = FALSE, results = 'asis'}
knitr::kable(head(metrics))
```

## Contributing

1.  Fork it ( https://github.com/glenn-m/promR/fork )
2.  Create your feature branch (git checkout -b my-new-feature)
3.  Make your changes
4.  Run `devtools::test()` to ensure tests are passing.
5.  Commit your changes (git commit -am 'Add some feature')
6.  Push to the branch (git push origin my-new-feature)
7.  Create a new Pull Request

## Contributors

- [Glenn McDonald](https://github.com/glenn-m)
- [Konrad Zdeb](https://github.com/konradedgar)
- [Tyler Littlefield](https://github.com/tyluRp)
