---
title: "Basic Usage"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  collapse = TRUE,
  comment = "#>"
)

# Enable httptest for vignette development
library(httptest)
start_vignette("basic-usage")

# Load package
library("promR")
```

# Introduction

Prometheus is an open-source software project recording real-time metrics using HTTP pull model [^1]. Prometheus records metrics in a time series database and allows for high-dimensionality. 

# Queries

The `promR` package offers `Promethous` class that provides two methods of sourcing data via instant and range query. The package also facilitates sourcing of the relevant metadata. With use of the sample host, the Prometheus class can be created in the following manner.

```{r example_class}
library("promR")
prom <- Prometheus$new(host = "http://demo.robustperception.io", port = 9090)
```


## Instant

The instant query sources the data for specific timestamp. The timestamp should be of class returned by `as.POSIXct`.

```{r example_instant}
# Timestamps can be in rfc3339 or unix format
metrics_instant <- prom$query(query = "go_goroutines", 
                              time = as.numeric(
                                as.POSIXct("2019-08-11 12:25:57 BST")))
```

```{r show_instant_results, echo=FALSE}
knitr::kable(metrics_instant)
```

## Range query

A range query permits sourcing of the data for a specific period according to a designated interval.

```{r example_range}
metrics_range <- prom$rangeQuery(
  query = "go_goroutines",
  start = as.numeric(as.POSIXct("2019-08-11 12:20:32 BST")),
  end = as.numeric(as.POSIXct("2019-08-11 12:30:46 BST")),
  step = "10s"
)
```

```{r show_range_results, echo=FALSE}
knitr::kable(head(metrics_range))
```

## Metadata

Metadata can be sourced using the `metadataQuery` call.

```{r metadata_example}
metrics_metadata <- prom$metadataQuery(match_target = '{job="node"}')
```

```{r show_metadata_example, echo=FALSE}
knitr::kable(head(metrics_metadata))
```

[^1]: For a detailed overview of the project refer to the project website [https://prometheus.io/](https://prometheus.io/).

```{r end-setup, include=FALSE}
# Close httptes vignette support
end_vignette()
```
